Learning and comparing functional connectomes between populations

### 2012-12-30 paper.tex
Iter intro

Brain functional connectivity captures the synchronization of distant
neural systems via correlations in brain activity. Given that brain
function emerges from the interaction of specialized units, functional
connectivity is an essential part of the description of brain function,
complementary to the localizationist picture emerging from the systematic
mapping of regions recruited in tasks. However, while activation mapping
has a well-defined standard analysis framework that enables
statistically-controlled comparisons across subjects \cite{friston1995},
group-level analysis of functional connectivity is still offers many
methodological challenges. Giving a picture of functional connectivity at
the subject level is by itself not straightforward, as the brain
comprises a myriad of interacting subsystems and must be decomposed in
simplified and synthetic representations: distributed functional networks
depicted by their spatial maps \cite{fox2005} or a connections linking
localized functional modules depicted as a graph \cite{bullmore2009}.
Here we focus on the latter: the functional connectome \cite{sporns2005}.

\cite{kelly2012}

Review paper giving technical guidelines.

BOLD signal during rest is typically just 5-10\% lower than during task-based
experiments \cite{raichle2006}.

Define what we call a functional connectome, and the term \emph{graph},
as well as its relation with an adjacency matrix.

@@

>>>>

% General introduction
Brain functional connectivity captures the synchronization of distant
neural systems via correlations in brain activity. Given that brain
function emerges from the interaction of specialized units, functional
connectivity is an essential part of the description of brain function,
complementary to the localizationist picture emerging from the systematic
mapping of regions recruited in tasks. However, while activation mapping
has a well-defined standard analysis framework that enables
statistically-controlled comparisons across subjects \cite{friston1995},
group-level analysis of functional connectivity is still offers many
methodological challenges. Giving a picture of functional connectivity at
the subject level is by itself not straightforward, as the brain
comprises a myriad of interacting subsystems and must be decomposed in
simplified and synthetic representations. An important view of brain
connectivity is that of distributed functional networks depicted by their
spatial maps \cite{fox2005}. Another no less important and complementary
view is that of connections linking localized functional modules depicted
as a graph \cite{bullmore2009}. This representation of brain connectivity
is often called the functional connectome \cite{sporns2005} and is the
focus of intense worldwide research efforts as it holds promises of new
insights in cognition and pathologies
\cite{greicius2008b,biswal2010,fox2010}.

% Give the scope of the paper and narrow it
The purpose of this paper is to review methodological progress in the
estimation and comparison of functional connectomes. It does not attempt
to be exhaustive, as the field is wide and moving rapidly, but details
specific tools and guidelines that, in the experience of the authors,
lead to controlled and powerful inter-subject comparisons. The paper is
focused on functional connectomes, in contrast to structural connectomes,
as the inference of functional connectivity from fluctuations in the
signal induces important specificities. While the notion of functional
connectome is often associated with the study of resting-state
\cite{biswal2010}, the methods presented in this paper are also relevant
for task-based studies. On the other hand, the paper has a focus on fMRI;
although the core concepts presented can be applied to MEG or EEG
\cite{stam2004}, additional specific problems such as source
reconstruction must be considered \cite{schoffelen2009}.

% Define terms
Define what we call a functional connectome, and the term \emph{graph},
as well as its relation with an adjacency matrix.

@@

% Give a layout of the paper
